Lesson 4
========================================================

***
```{r}
setwd('~/Downloads')
getwd()
```

### Scatterplots and Perceived Audience Size
Notes:

***

### Scatterplots
Notes:

```{r Scatterplots}
library(ggplot2)
pf <- read.csv('pseudo_facebook.tsv',sep='\t')

qplot(x=age,y=friend_count,data=pf)

```

***

#### What are some things that you notice right away?
Response:
一般较多好友数的用户聚集在低年龄段，20岁左右。图中比较明显的直线可能是用户随意填写的年龄，例如69，100。
***

### ggplot Syntax
Notes:

```{r ggplot Syntax}
ggplot(aes(x=age,y=friend_count),data=pf) +geom_point() +
  xlim(13,90)


```
```{r}
summary(pf$age)
```

***

### Overplotting
Notes:

```{r Overplotting}
ggplot(aes(x=age,y=friend_count),data=pf) +
  geom_jitter(alpha=1/20) +
  xlim(13,90)
```

#### What do you notice in the plot?
Response:
从图中可以看到，年轻用户的好友数并没有之前看到的那么高，大多数年轻用户的好友数低于1000；在69岁处仍可以看到有一个峰值，虽然模糊了许多，因为我们把alpha设置为1/20，也就是一个圆圈变成20个点。但是看起来69岁和25，26岁年龄组的用户具有可比性。
***

### Coord_trans()
Notes:

```{r Coord_trans()}
ggplot(aes(x=age,y=friend_count),data=pf) +
  geom_point(alpha=1/20,position = position_jitter(h=0)) +
  xlim(13,90) +
  coord_trans(y="sqrt")
```

#### Look up the documentation for coord_trans() and add a layer to the plot that transforms friend_count using the square root function. Create your plot!

```{r}

```

#### What do you notice?

***

### Alpha and Jitter
Notes:

```{r Alpha and Jitter}
ggplot(aes(x=age,y=friendships_initiated),data = pf) +
  geom_jitter(alpha=1/20,position = position_jitter(h=0)) +
  coord_trans(y='sqrt') +
  xlim(13,90)


```

***

### Overplotting and Domain Knowledge
Notes:

***

### Conditional Means
Notes:

```{r Conditional Means}
library(dplyr)
age_groups <- group_by(pf,age)
pf.fc_by_age <- summarise(age_groups,
                          friend_count_mean = mean(friend_count),
                          friend_count_median = median(friend_count),
                          n = n())

pf.fc_by_age <- arrange(pf.fc_by_age,age)
head(pf.fc_by_age)


```

Create your plot!

```{r Conditional Means Plot}
ggplot(aes(x=age,y=friend_count_mean),data=pf.fc_by_age) +
  geom_line()
```

***

### Overlaying Summaries with Raw Data
Notes:

```{r Overlaying Summaries with Raw Data}
ggplot(aes(x=age,y=friend_count),data=pf) +
  coord_cartesian(xlim = c(13,70),ylim = c(0,1000)) +
  geom_point(alpha = 0.05,
             position = position_jitter(h=0),
             color = 'orange') +
  geom_line(stat = 'summary',fun.y = mean) +
  geom_line(stat = 'summary',fun.y = quantile, fun.args = list(probs = .1),
            linetype = 2,color = 'blue') +
  geom_line(stat = 'summary',fun.y = quantile, fun.args = list(probs = .5),
            color = 'blue') +
  geom_line(stat = 'summary',fun.y = quantile, fun.args = list(probs = .9),
            linetype = 2,color = 'blue') 
```

#### What are some of your observations of the plot?
Response:

***

### Moira: Histogram Summary and Scatterplot
See the Instructor Notes of this video to download Moira's paper on perceived audience size and to see the final plot.

Notes:

***

### Correlation
Notes:

```{r Correlation}
cor(pf$age,pf$friend_count)

cor.test(pf$age,pf$friend_count,method = 'pearson')

with(pf,cor.test(age,friend_count,method = 'pearson'))
```

Look up the documentation for the cor.test function.

What's the correlation between age and friend count? Round to three decimal places.
Response:

***

### Correlation on Subsets
Notes:

```{r Correlation on Subsets}
with(subset(pf,age <= 70) , cor.test(age, friend_count,
                                        method = 'spearman'))
```

***

### Correlation Methods
Notes:

***

## Create Scatterplots
Notes:

```{r}
ggplot(aes(x = www_likes_received,y = likes_received),data = pf) +
  geom_point() +
  xlim(0,quantile(pf$www_likes_received,0.95)) +
  ylim(0,quantile(pf$likes_received,0.95)) +
  geom_smooth(method = 'lm', color = 'red')
```

***

### Strong Correlations
Notes:

```{r Strong Correlations}
cor.test(pf$www_likes_received,pf$likes_received)
```

What's the correlation betwen the two variables? Include the top 5% of values for the variable in the calculation and round to 3 decimal places.

```{r Correlation Calcuation}

```

Response:

***

### Moira on Correlation
Notes:

***

### More Caution with Correlation
Notes:

```{r More Caution With Correlation}
install.packages('alr3')
library(alr3)
data("Mitchell")
?Mitchell
head(Mitchell)
```

Create your plot!

```{r Temp vs Month}
ggplot(aes(x=Month,y=Temp),data = Mitchell) + 
  geom_point()


```

***

### Noisy Scatterplots
a. Take a guess for the correlation coefficient for the scatterplot.

b. What is the actual correlation of the two variables?
(Round to the thousandths place)

```{r Noisy Scatterplots}
cor.test(Mitchell$Month,Mitchell$Temp)

```

***

### Making Sense of Data
Notes:

```{r Making Sense of Data}
ggplot(aes(x=Month,y=Temp),data = Mitchell) + 
  geom_point() +
  scale_x_continuous(breaks = seq(0,203,12))
```

***

### A New Perspective

What do you notice?
Response:
每年的温度变化呈现正弦图像
Watch the solution video and check out the Instructor Notes!
Notes:

***

### Understanding Noise: Age to Age Months
Notes:

```{r Understanding Noise: Age to Age Months}
ggplot(aes(x=age,y=friend_count_mean),data=pf.fc_by_age) +
  geom_line()
```

***

### Age with Months Means

```{r Age with Months Means}
pf$age_with_months <- pf$age + (1 - pf$dob_month/12)
```

Programming Assignment
```{r Programming Assignment}
age_bymonth_groups <- group_by(pf,age_with_months)
pf.fc_by_agemonth <- summarise(age_bymonth_groups,
                          friend_count_mean = mean(friend_count),
                          friend_count_median = median(friend_count),
                          n = n())

pf.fc_by_agemonth <- arrange(pf.fc_by_agemonth,age_with_months)
head(pf.fc_by_agemonth)

```

***

### Noise in Conditional Means

```{r Noise in Conditional Means}
ggplot(aes(x=age_with_months,y=friend_count_mean),data = pf.fc_by_agemonth) + 
  geom_line() +
  coord_cartesian(xlim = c(13,70),ylim = c(0,450))
  
```

***

### Smoothing Conditional Means
Notes:

```{r Smoothing Conditional Means}
p1 <- ggplot(aes(x=age,y=friend_count_mean),
       data=subset(pf.fc_by_age,age<71)) + 
  geom_line()

p2 <- ggplot(aes(x=age_with_months,y=friend_count_mean),
       data = subset(pf.fc_by_agemonth,age_with_months<71)) + 
  geom_line()

library(gridExtra)
grid.arrange(p2,p1,ncol = 1)
```

***

### Which Plot to Choose?
Notes:

***

### Analyzing Two Variables
Reflection:
通过降低容器大小并增加容器数量，我们减少了估计每个条件平均的数据，噪声更多的图形是因为我们选择了更精细的容器。
***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!

